Brief notes on erosion

### 2019-05-21 docs/proposals/ErosionWhitePaper.tex
NM

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Physics-Based Understanding of Viscous Erosion}
\todo[inline]{Characterizing anisotropy}
\todo[inline]{Coarse-grained transport (anomalous diffusion)}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Physics-Based Understanding of Viscous Erosion}

Armed with these new tools, we plan to investigate how erosion alters a porous medium through a reshaping process that occurs on the grain scale. Initial investigations showed that, as bodies erode and reduce in size, the permeability of the medium increases. The rate of increase, however, cannot be explained by the reduction in grain size alone, as the reshaping and associated formation of channels are vital elements. The new methods will allow us to examine these features in more detail. In particular, we anticipate that erosion may also lead to the development of {\bf anisotropic} permeability, as the medium gradually reconfigures to transmit flow more easily in the direction of the initial flow. The new methods will allow us to characterize the changes in permeability and anisotropy especially in nearly-touching body configurations, in more dense packings, and eventually in configurations of mobile and/or sedimenting grains.

\todo[inline]{Coarse-grained transport (anomalous diffusion)}
\todo[inline]{Nick: I am not an expert on anomalous diffusion. Bryan, do you want to write this paragraph?}
